%----------------------------------------------------------------------------------------
%	ABSTRACT PAGE
%----------------------------------------------------------------------------------------

\begin{abstract} \label{chap_abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents

The bachelor thesis aims to construct several electrical circuits of development board, sensors and lights and develop voice-enabled smart home modules. The first step design a hardware solution and the physical implementation of individual sensors and lights with development boards. As the next step, the development boards are programmed and built \textit{engine} as a software environment for data communication, data storage and voice-enabled modules. Furthermore, a VoiceKit is connected to the \textit{engine} to allow a user to control modules by voice. The central part of the project is a web page visualizing all states of components, listed voice commands, currently uttered user commands, and graph data from sensors. The outcome of this project is a functional example use of modules in a basic smart home.

    \begin{abstract_cz} \label{chap_abstract_cz}
        % \addchaptertocentry{\abstractname} % Add the abstract to the table of contents
        
        Tato bakalářská práce si klade za cíl zkonstruovat několik elektrických obvodů vývojové desky, senzorů a světel a vyvinout hlasové inteligentní domácí moduly. Prvním krokem je návrh hardwarového řešení a fyzická implementace jednotlivých senzorů a světel s vývojovými deskami. Jako další krok jsou vývojové desky naprogramovány a vytvořen \textit{engine} jako softwarové prostředí pro datovou komunikaci, ukládání dat a hlasové moduly. Dále je k \textit{engine} připojen VoiceKit, který umožňuje uživateli ovládat moduly hlasem. Významnou částí projektu je webová stránka zobrazující všechny stavy komponent, uvedené hlasové příkazy, aktuálně vyslovené uživatelské příkazy a data grafů ze senzorů. Výsledkem tohoto projektu je funkční ukázkové použití modulů v základní inteligentní domácnosti.
        
    \end{abstract_cz}

\end{abstract}

